From Freebase to Wikidata: The Great Migration

### 2016-01-29 paper.tex
Reworked Section 3.4.

\subsection{Long-term maintenance}
\label{sec:longtermmaintenance}

Wikidata's editing community is in charge of the project's content. This includes collecting the
data as well as long-term maintenance of it. Data needs to be updated as the world changes, but also
kept free of vandalism. An increase in the amount of data comes with an increase in maintenance
cost for the community. Simply ingesting the Freebase data would have meant overwhelming the
existing editors and thereby harming the project in the long run. To counter this, a~significant
increase in the amount of data needs to go along with either an increase in the number of editors
or provision of tools to assist the existing editors to allow them to be more effective. With the
Primary Sources Tool, we aim to help grow the community in step with the amount of data. It is
useful as a~means to get more people to edit because it lowers the barrier to entry. It does this
by making it easier to find potential edits. At the same time, it helps make some of the existing
editors more effective by allowing them to add statements with a~single click.

>>>>

\subsection{Long-Term Maintenance}
\label{sec:longtermmaintenance}

Wikidata's editing community is in charge of the project's content. This includes collecting the
data as well as long-term maintenance of it. Data needs to be updated as the world changes, but also
kept free of vandalism. An increase in the amount of data comes with an increase in maintenance
cost for the community. Simply ingesting the Freebase data would have meant overwhelming the
existing editors and thereby harming the project in the long run. To counter this, a~significant
increase in the amount of data needs to go along with either an increase in the number of editors
or provision of tools to assist the existing editors to allow them to be more effective. With the
\emph{Primary Sources Tool}, we aim at helping grow the community in step with the amount of data. It is
useful as a~means to get more people to edit, as it lowers the barrier to entry by
making it easier to find potential edits. At the same time, it helps make some of the existing
editors more efficient by allowing them to add statements with a~single click.
